Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/survey_details.tex
some work improving appendix E tables & figures (not done)

\todo{make this table prettier! fix vertical spacing}

\begin{table}[h!]
\centering
\caption{General questions about the conference program}
\label{tab:survey_program}
{\scriptsize
\begin{tabular}{|l|cccccc|}
\hline
{\bf Question} &
{\bf strongly} &
{\bf somewhat}  &
{\bf agree} &
{\bf somewhat}  &
{\bf strongly}  &
{\bf Total} \\
&
{\bf disagree} &
{\bf disagree} &
&
{\bf agree} &
{\bf agree} &
\\ \hline
The plenary sessions had a good&
5 &
3 &
8 &
11 &
18 &
45 \\
\hspace{.2cm}mix of topics and speakers. &
 &
 &
 &
 &
 &
 \\
The balance was right between  &
6 &
2 &
7 &
9 &
21 &
45 \\
\hspace{.2cm}talks, panels, and lightning talks. &
&
 &
 &
 &
 &
 \\
There was sufficient time for discussion. &
6 &
6 &
8 &
9 &
16 &
45 \\
\hline
\end{tabular}
}
\end{table}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{figures/SurveyFig1rev}
  \caption{The plenary sessions had a good mix of topics and speakers.\label{fig:SFig1}}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{figures/SurveyFig2rev}
  \caption{The balance was right between talks, panels, and lightning talks.\label{fig:SFig2}}
\endminipage\hfill
\minipage{0.35\textwidth}%
  \includegraphics[width=\linewidth]{figures/SurveyFig3rev}
  \caption{There was sufficient time for discussion.\label{fig:SFig3}}
\endminipage
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{Value of meeting parts}
\label{tab:survey_parts}
\begin{tabular}{|l|c|}
\hline
{\bf Answer} &
{\bf Count} \\ \hline
Plenary &
19 \\
Panel &
14 \\
Working Groups &
36 \\
Other &
5 \\
Total &
74 \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{General questions about the conference program}
\label{tab:survey_program}
{\scriptsize
\begin{tabular}{@{}lcccccc@{}}
\toprule
\multirow{2}{*}{Question} & strongly & somewhat & agree & somewhat & strongly &
\multirow{2}{*}{Total} \\
& disagree & disagree & & agree & agree & \\
\midrule
\rowcolor{lightgray} The plenary sessions had a good & & & & & & \\
\rowcolor{lightgray} mix of topics and speakers. &
\multirow{-2}{*}{5} &
\multirow{-2}{*}{3} &
\multirow{-2}{*}{8} &
\multirow{-2}{*}{11} &
\multirow{-2}{*}{18} &
\multirow{-2}{*}{45} \\
The balance was right between &
\multirow{2}{*}{6} &
\multirow{2}{*}{2} &
\multirow{2}{*}{7} &
\multirow{2}{*}{9} &
\multirow{2}{*}{21} &
\multirow{2}{*}{45} \\
talks, panels, and lightning talks. & & & & & & \\
\rowcolor{lightgray} There was sufficient time for discussion. &
6 &
6 &
8 &
9 &
16 &
45 \\
\bottomrule
\end{tabular}
}
\end{table}

@@

\begin{figure}[!htb]
    \begin{subfigure}{0.34\textwidth}
    \includegraphics[width=\linewidth]{figures/SurveyFig1rev}
    \caption{The plenary sessions had a good mix of topics and speakers.}
    \label{fig:SFig1}
    \end{subfigure}
    ~
    \begin{subfigure}{0.32\textwidth}
    \includegraphics[width=\linewidth]{figures/SurveyFig2rev}
    \caption{The balance was right between talks, panels, and lightning talks.}
    \label{fig:SFig2}
    \end{subfigure}
    \begin{subfigure}{0.25\textwidth}
    \includegraphics[width=\linewidth]{figures/SurveyFig3rev}
    \caption{There was sufficient time for discussion.}
    \label{fig:SFig3}
    \end{subfigure}
    \caption{Responses to generate questions about the conference program}
\end{figure}

@@

\begin{table}[h!]
\rowcolors{1}{}{lightgray}
\centering
\caption{Value of meeting parts}
\label{tab:survey_parts}
\begin{tabular}{|l|c|}
\hline
{\bf Answer} &
{\bf Count} \\ \hline
Plenary &
19 \\
Panel &
14 \\
Working Groups &
36 \\
Other &
5 \\
Total &
74 \\
\hline
\end{tabular}
\end{table}
